---
title: "Trial"
author: "Handing Zhang"
date: "11/29/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.align = "center")
```

Packages
```{r packages, include=FALSE}
pacman::p_load(gutenbergr, dplyr, tidytext, janeaustenr, stringr, 
               scales, ggplot2, tidyr, textdata, wordcloud, reshape2, tidyverse)
``` 

## Download Data and Explore
Download the Book **Sea-Wolf** from gutenberg package.
```{r}
sea <- gutenberg_download(1074)
```

Turn the dataset to a tidy form.
```{r}
tidy_sea <- sea %>%
  unnest_tokens(word, text) %>%  # output is word column, input is from text column in original sea dataset.
  anti_join(stop_words) # get rid of stop words

tidy_sea <- sea %>% 
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text,       # add a chapter column to mark chapter number.
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE))))%>%
   unnest_tokens(word, text) %>% 
   anti_join(stop_words) # get rid of stop words.
```

We start by looking at the most frequently appeared words in the book.
```{r}
tidy_sea %>% 
  count(word, sort = T)
```

let's also visualize the words that appeared more than 100 times in a descending order.
```{r plot1}
tidy_sea %>% 
  count(word, sort = T) %>% 
  filter(n >= 100) %>% 
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() + 
  labs(y = NULL)
```

Let's calculate the frequency of each word
```{r frequency of words}
frequency <- tidy_sea %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%  
  ## eliminate underscores around words so that _apple_ is treated thesame as apple.
  count(word) %>% 
  mutate(proportion = n / sum(n)) %>% 
  arrange(desc(proportion))

frequency
```

## Sentimental Analysis

Get sentiment words from sentiment lexicons "AFINN" "BING" "NRC"
```{r}
afinn <- get_sentiments("afinn")
bing <- get_sentiments("bing")
```


```{r}
# textdata::lexicon_nrc(delete = TRUE)
# nrc <- textdata::lexicon_nrc()
# write.csv(nrc, "/Users/handingzhang/Desktop/mssp/MA 615/Homework/615-Assignment-4/nrc.csv", row.names = FALSE)
nrc <- read.csv("nrc.csv")
```


Now let's see the most frequently used word with "joy" sentiment according to nrc in **The Sea-wolf**
```{r}
nrc_joy <- nrc %>% 
  filter(sentiment == "joy")
# nrc_joy
# we take out all words with joy sentiment from nrc.


# use inner_join to join the rows of tidy_sea that has the according elements
tidy_sea %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)

```



We get a sentiment score for each 80 lines by the number of positive and negative sentimental words according to nrc.
```{r}

sea_sentiment <- tidy_sea %>%
  inner_join(bing) %>%
  count(index = linenumber %/% 80, sentiment) %>%  
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)


```



Plot the sentiment score by nrc measure against timeline of the book by index of 80 lines.
```{r plot2}
ggplot(sea_sentiment, aes(index, sentiment)) +
  geom_col(show.legend = FALSE, color = "blue")

```

We see in general the sentiment is quite negative, but we also notice that at one point the sentinent is fairly high.
```{r}
which(sea_sentiment$sentiment >= 10)
```
There might be a positive plot happening between line 102 * 80 = 8160 and 103 * 80 = 8240.



Now let's compare the three lexicons.
```{r}

# Measured by afinn
sea_afinn <- tidy_sea %>% 
  inner_join(afinn) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

# Measured by bing and nrc
sea_bing_and_nrc <- bind_rows(
  tidy_sea %>% 
    inner_join(bing) %>%
    mutate(method = "Bing"),
  tidy_sea %>% 
    inner_join(nrc %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)


```



Compare the visualization of sentiment measurements by the three methods
```{r plot3}
bind_rows(sea_afinn, 
          sea_bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```





Count the number of each word in each sentiment for being.
```{r}
sea_bing_word_counts <- tidy_sea %>%
  inner_join(bing) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()


sea_bing_word_counts
```




```{r plot4}
sea_bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

```




Make a word cloud
```{r plot5}
tidy_sea %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```


Word cloud with positive sentiments blow and neggative above.
```{r}

tidy_sea %>%
  inner_join(bing) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```




